\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
Jiang citation
stuffs

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
to us that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detal. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
due to complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

\todo{more}

Previous attempts to map Sol d from the exoplanet community have suggested 
the presence of localized surface features, but their resolving power has been 
severely limited by the duration of observations \citep{Cowan2009}. 
\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
phases, enabling a level of spatial and temporal resolving power that is 
unprecedented in the history of exoplanet phase mapping.

Moreover, recent advances in the computational tractability of this data analysis problem 
have made the reconstruction of detailed maps more feasible than ever. 
\todo{(describe how STARRY works - fast analytic computation of spherical harmonics)}
\todo{(also maybe say something about Cowan approach)}

>>>>

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
to us that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

Previous attempts to map Sol d from the exoplanet community have suggested 
the presence of localized surface features, but their resolving power has been 
severely limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
phases, enabling a level of spatial and temporal resolving power that is 
unprecedented in the history of exoplanet phase mapping.

Moreover, recent advances in the computational tractability of this data analysis problem 
have made the reconstruction of detailed maps more feasible than ever. 
\cite{Luger2019} developed a \todo{more more more}
\cite{Haggard2018}
